One-step, three-factor authentication with in-ear EEG

### 2016-12-05 paper.tex
Added future work adn conclusion

\begin{table}[h]
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\centering
\begin{tabular}{l|rr|rr|rr}
\textbf{Task} & \textbf{Left Ear} &  & \textbf{Right Ear} &  & \textbf{Fp1} & \\
\hline
 & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR}\\
\hline
Breathe & 0 & 0 & 0 & 0 & 0 & 0\\
Breathe - Open & 0.039 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
Song & 0 & 0 & 0 & 0 & 0 & 0\\
Song - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Speech & 0 & 0 & 0 & 0 & 0 & 0\\
Listen - Tone & 0 & 0 & 0 & 0.009 & 0 & 0\\
Listen - ASSR & 0 & 0 & 0 & 0 & 0 & 0\\
Face & 0 & 0 & 0 & 0.002 & 0 & 0\\
Sequence & 0 & 0 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

@@

\begin{table}[h]
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\centering
\begin{tabular}{lrrr}
\textbf{Task} & \textbf{Right Ear} & \textbf{Left Ear} & \textbf{Fp1}\\
\hline
Breathe & 0 & 0.240 & 0\\
Breathe - Open & 0.254 & 0.129 & 0\\
Sport & 0.222 & 0.135 & 0\\
Song & 0 & 0.211 & 0\\
Song - Open & 0 & 0.166 & 0\\
Speech & 0.311 & 0.116 & 0\\
Listen - Tone & 0 & 0.333 & 0\\
Listen - ASSR & 0.322 & 0.078 & 0\\
Face & 0.355 & 0.055 & 0\\
Sequence & 0.433 & 0 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

@@

>>>>

\begin{table}[h]
\centering
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\begin{tabular}{l|rr|rr|rr}
\textbf{Task} & \textbf{Left Ear} &  & \textbf{Right Ear} &  & \textbf{Fp1} & \\
\hline
 & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR}\\
\hline
Breathe & 0 & 0 & 0 & 0 & 0 & 0\\
Breathe - Open & 0.039 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
Song & 0 & 0 & 0 & 0 & 0 & 0\\
Song - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Speech & 0 & 0 & 0 & 0 & 0 & 0\\
Listen - Tone & 0 & 0 & 0 & 0.009 & 0 & 0\\
Listen - ASSR & 0 & 0 & 0 & 0 & 0 & 0\\
Face & 0 & 0 & 0 & 0.002 & 0 & 0\\
Sequence & 0 & 0 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

@@

\begin{table}[h]
\centering
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\begin{tabular}{lrrr}
\textbf{Task} & \textbf{Right Ear} & \textbf{Left Ear} & \textbf{Fp1}\\
\hline
Breathe & 0 & 0.240 & 0\\
Breathe - Open & 0.254 & 0.129 & 0\\
Sport & 0.222 & 0.135 & 0\\
Song & 0 & 0.211 & 0\\
Song - Open & 0 & 0.166 & 0\\
Speech & 0.311 & 0.116 & 0\\
Listen - Tone & 0 & 0.333 & 0\\
Listen - ASSR & 0.322 & 0.078 & 0\\
Face & 0.355 & 0.055 & 0\\
Sequence & 0.433 & 0 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

@@

\section{Proposed Future Work}

In expanding on the feasibility study we describe above, 
our first task comprises of collecting data from more subjects,
ideally for a subject population of 30.
In addition, we hope to collect more diverse data,
by taking regular samples over a period of a few weeks,
and in a variety of circumstances. Our goal here is gague the stability
of EEG readings over time, and outside of lab environments.
If the system will need to be calibrated occasionally, these readings
could help us understand how frequently such calibration sessions
might need to take place

Toward this end, propose to build a working, real-time passthought authenticator.
After performing an initial calibration setup, similar to our pilot study's protocol, above,
we will send subjects home with their custom-fit ear EEG, and ask them to use the device to authenticate
two to three times a day for a week.
(We may ask subjects to set a recurring event on their calendar to remind them, 
or pay subjects in accordances with how frequently they authenticated, up to some reasonable maximum).
After a week, subjects will return to the lab to return their equipment, debrief about their experience, and recieve payment. We will use this opportunity to walk subjects through a relatively detailed post-interview,
during which we will focus on their experiences with the device (things they may not have posted to others on the platform).

The goal of this work is to understand both the technical issues facing ear-EEG authentication
(Does the system work reliably? When and why does it fail?), and the usability issues
(How do subjects feel about having an EEG device in their ear throughout the day?).
Finally, this closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine
co-adapt during multiple authentication attempts.

After testing that our system can reliably provide authentication with a 
a secret passthought (knowledge) and unique EEG signal (inherence),
we will turn our attention to the final, third factor: posession
(of the unique, custom-fit ear EEG device).
We propose to cryptographically assure device posession
by assigning each custom-fit electrode a unique public/private keypair. 
User accounts could be associated with an earpiece's public key,
and authentication attempts from the earpiece could be signed its
its private key, producing authentication attempts that are not
forgeable by other custom-fit earpieces.

\section{Conclusion}
At the end of the proposed project,
we will have developed an authentication attempt that provides three factors
(knowledge, inherence and posession) in a single authentication attempt.
This work could lead to authentication strategies that are both more secure
and more useable than traditional, password-based authentication.
